Stabilization-Free Virtual Element Methods

### 2023-06-29 reports/response1.tex
typo
adjust mesh assumption (A2)

The authors greatly appreciate the questions and concerns the reviewers have raised in the reports, as well as the careful reading. 
We have revised our manuscript in terms of your suggestions and polished the writing throughout. 
Other than some single word typos, important changes are highlighted in colored texts in this revision.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. By the numerical results on the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
matrix,
the VEMs without extrinsic stabilization are competitive with respect to other existing VEMs.
Now we emphasize that
\begin{itemize}
\item
In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and reduces its practicality.
\item 
Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
\end{itemize}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. The performance of our VEMs and other existing VEMs is similar for simple benchmarks.
Now we emphasize that
\begin{itemize}
\item
In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and reduces its practicality.
\item 
Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
\end{itemize}

>>>>

The authors greatly appreciate the questions and concerns the reviewers have raised in the reports, as well as the careful reading. 
We have revised our manuscript in terms of your suggestions. 
Other than some single word typos, important changes are highlighted in colored texts in this revision.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. By the numerical results on the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
matrix,
the VEMs without extrinsic stabilization are competitive with respect to other existing VEMs.
Now we emphasize that
\begin{itemize}
\item
In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and will reduce its practicality.
\item 
Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
\end{itemize}

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Yes. The performance of our VEMs and other existing VEMs is similar for simple benchmarks.
Now we emphasize that
\begin{itemize}
\item
In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and will reduce its practicality.
\item 
Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
\end{itemize}

### 2023-06-29 stabfreevem_sinum.tex
adjust mesh assumption (A2)

\section{Introduction}
An additional stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form~\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
% , while the stabilization term also brings about some problems. 
The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
% The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization term dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems. 
\XH{
In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and reduces its practicality.}

@@

% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
% the analysis is rather elaborate. 
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
We intend to construct VEMs \XH{without extrinsic stabilization} in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
The key to construct VEMs \XH{without extrinsic stabilization} is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
\XH{To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.}
% $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
% Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require that
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

 \item[(A2)] There exists a quasi-uniform simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
\end{itemize}

@@

For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
\[
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
\]

>>>>

\section{Introduction}
An additional stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form~\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
% , while the stabilization term also brings about some problems. 
The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
% The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization term dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems. 
\XH{
In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and will reduce its practicality.}

@@

% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
% the analysis is rather elaborate. 
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
We intend to construct VEMs \XH{without extrinsic stabilization} in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
The key to construct VEMs \XH{without extrinsic stabilization} is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then an additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
\XH{To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.}
% $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
% Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require that
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for the differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

 \item[(A2)] \XH{There exists a shape-regular simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$. For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$. Assume simplicial partition $\mathcal T_K$ is quasi-uniform.}
\end{itemize}

@@

% For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. 
Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
\[
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
\]
